Representation Learning for Generalized Planning - SAT Encodings

### 2021-05-06 doc/paper/paper.tex
little clean up
updated paper ¡

\paragraph{Bad'}

@@

We here assume that all instances $P$ of the generalized problem have a set of actions $A$.
We denote by $(s, a, s') \in T$ tuples of state, action, and possible state $s'$ resulting from executing $a$ in $s$.

@@

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
 \item $Good(s, a, s')$ for $s$ alive, solvable, and $a \in A$.

@@

\smallpar{C1}
The policy has to be complete with respect to all possible actions applicable in s:
\begin{align}
\bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
\end{align}

\smallpar{C1}
The policy has to be complete with respect to all alive states:
\begin{align}
\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
\end{align}

@@

\smallpar{C5-6}
Good pairs $(s, a)$ can be distinguished from bad pairs $(s, a)$.
%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
%of two different equivalence classes such that $(s, s') \not\in \badtx$
%(which implies that $s'$ is solvable). Then,
\begin{align}
 Good(s, a) \rightarrow Good(t, a) \lor
 D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \not\in \badtx$.} \\
 Good(s, a) \rightarrow D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \in \badtx$.}
\end{align}

@@

\smallpar{C7 (Optional)}
Goals are distinguishable from non-goals.
\begin{align}
\bigvee_{f \in D1(s, s')} Select(f),&\;\; \text{for $s$ goal, $s$ not a goal}
\end{align}

\subsubsection{Soft Constraints}
We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.

>>>>

\paragraph{Bullet points}
\begin{itemize}
\item Learning generalized policies in unsupervised FOND domains from small examples.
\item FOND encoding, introducing Good(s, a) features to deal with non-determinism. Where $a \in A$, and $A$ is not required to be fixed. However, if $A$ is fixed we show a way to exploit it, reducing the number of transitions to distinguish.
\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
\item Empirical results with five domains: Chase, Shoot, Space Invaders, Delivery, Wumpus world.
\item Incremental policy learning, to address the scalability problem. First a random sample is taken from the whole graph and the policy is then refined incrementally by iteratively increasing the sample size. The strategy for increasing the size of the sample can be goal-directed or random.
%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
\item Use of a uniform grammar for the different grid domains.
\end{itemize}

@@

We here assume that all instances $P$ of the generalized problem have a set of actions $A$. We do not need $A$ begin fixed.
We denote by $(s, a, s') \in T$ tuples of state, action, and possible state $s'$ resulting from executing $a$ in $s$.

@@

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
 \item $Good(s, a, s')$ for $s$ alive, $s'$ solvable, and $(s, a, s') \not\in \badtx$.

@@

\smallpar{C1}
The policy has to be complete with respect to all alive states:
\begin{align}
\bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
\end{align}

@@

\smallpar{C5-6}
Good transitions $(s, a, s')$ can be distinguished from bad transitions $(s, a, s')$.
%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
%of two different equivalence classes such that $(s, s') \not\in \badtx$
%(which implies that $s'$ is solvable). Then,
Let $(s, a, s')$ and $(t, b, t')$ be \emph{representative} transitions
of two different equivalence classes such that $(s, a, s') \not\in \badtx$
(which implies that $s'$ is solvable). Where $a, b \in A$. Then,
\begin{align}
 Good(s, a, s') \rightarrow Good(t, b, t') \lor
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
 Good(s, a, s') \rightarrow
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
\end{align}

@@

\smallpar{C7 (Optional)}
The transitions $(s, a, s')$ and $(s, a, t')$ will be treated as equivalent. In $C5-6$ if $a=b$ and $s=t$ we don't require this transitions to be distinguished.

\smallpar{C8}
Good pairs $(s, a)$ implies at least one transition $(s, a, s')$ labeled as good.
\begin{align}
\bigvee_{s' \text{ s.t. } (s, a, s') \in T \setminus \badtx} Good(s, a, s'),&\;\; \text{for $(s, a)$ where $s$ alive.}
\end{align}

\smallpar{C9 (Optional)}
Goals are distinguishable from non-goals.
\begin{align}
\bigvee_{f \in D1(s, s')} Select(f),&\;\; \text{for $s$ goal, $s$ not a goal}
\end{align}

\smallpar{C10 (Optional)}
All selected features need to have some Good transition that takes them to $0$:
\begin{align}
 Selected(f) \rightarrow \bigvee_{(s, a, s') \in Z(f)} Good(s, s'),&\;\; \text{for $f$ in pool}
\end{align}

\noindent where $Z(f)$ is the set transitions starting in an alive state that change the denotation of $f$ from something
larger than 0 to 0.

\subsubsection{Soft Constraints}
\smallpar{C11}
We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.

\smallpar{C12 (Optional)}
If no action is good in state $s$ alternatively we can set the state as $Bad(s)$. Then  post a constraint $\neg Bad(s)$, with weight equal to one. Then the constraint $C1$ changes,
\begin{align}
Bad(s) ~ or~ \bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
\end{align}

\noindent Notice that now the policy is complete in domains where an state can not be solved or has not any $Good(s, a)$.

\section{Empirical Results}

\subsection{Chase}

\subsection{Shoot}

\subsection{Space Invaders}

\subsection{Delivery}

\subsection{Wumpus world}
